### 2015-04-23 paper.tex
Write conclusions

>>>>

\subsection*{Conclusions}

The performance and near-wake for a 1:6 scale DOE Reference Model 2 cross-flow
turbine was measured in a towing tank. Performance was assessed for Reynolds
number dependence, showing a convergence to a weakly $Re$-dependent linear
regime at approximately $Re_D \approx 1 \times 10^6$ or $Re_{c,\mathrm{ave}}
\approx 2 \times 10^5$. Comparison was made between this turbine and the higher
solidity UNH-RVAT, tested in nearly identical conditions, which showed similar
Reynold number thresholds but a flatter linear regime, likely to due virtual
camber of the higher chord-to-radius ratio of the UNH-RVAT blades.

The wake at $x/D=0.93$ downstream was shown to be relatively symmetrical and
lacked the evidence of strong blade stall, which once again differentiates this
turbine from the UNH-RVAT. Terms from the mean kinetic energy transport equation
were also computed in this $y$--$z$ plane, showing the relative importance of
the vertical advection compared with turbulent transport terms at this location.
It is interesting to note that though the turbine is a more effective energy
converter than the UNH-RVAT, its wake recovery may in fact be slower due to
weaker blade tip vortex shedding.

The effects of parasitic drag from blade support struts on turbine performance
were measured by rotating the turbine without blades while stationary and while
towing. It is shown that these losses---even for a streamlined hydrofoil
strut---can become significant quickly at higher tip speed ratios---up to an
approximate 5 percentage point decrease in power coefficient at a tip speed
ratio of 5. These measurements were repeated with a set of high-drag cylindrical
struts, which as expected, prevented the turbine from producing any mechanical
power at any tip speed ratio. Nevertheless these measurements provide important
validation data for both high and low fidelity numerical performance prediction
models, allowing researchers to test models without blade effects.

This data, along with the code for processing and visualization, is provided
openly via a Creative Commons license, and is available from
\cite{Bachant2015-RM2-data}. The authors hope that this can provide
opportunities for extensive validation of predictive tools for the complex
unsteady flow physics of cross-flow turbines.
